---
title: "Segmentation of natural color images original"
subtitle: " RPubs by RStudio "
author: "Ivan Lizarazo"
date: "15 June 2020"
output: html_notebook
---

Ensayo de Segmentación de imágenes RGB, basado en el ejercicio publicado por [Ivan Lizarazo](https://rpubs.com/ials2un/segment_rgb) en formato de Notebook.

```{r}
library ("rasterVis") |> suppressPackageStartupMessages()
library ('OpenImageR') |> suppressPackageStartupMessages()
library ('RImagePalette') |> suppressPackageStartupMessages()
library("raster") |> suppressPackageStartupMessages()
source(file = "indices_vegetacion_RGB.R")
```

1.  Reading the image to analyze

The image has been downloaded from the NASA Earth Observatory website. It illustrates the diverse agricultural landscape in the western part of Minas Gerais state in Brazil.

Se lee la imagen a analizar:

```{r, warning = FALSE}
(crops <- stack("~/giserias/conchalito-vuelo2/conchal_10Q.tif"))
(crops <- stack("~/giserias/conchalito-vuelo2/RPubs_cropsQ.tif"))
```

Vemos la imagen cargada:

```{r}
plotRGB(crops, 1, 2, 3)
```

## True Color Vegetation Indices

Thanks to Matthias Forkel we can use a nice palette for vegetation indices:

```{r}
colores <- function(n) {
    .fun <- colorRampPalette(c("chocolate4", "orange", "yellow", "grey", "green", "green3", "darkgreen"))
    col <- .fun(n)
    return(col)
}

```

Let’s calculate the ExG index:

```{r}
# For the crops image red = 1, green=2, blue = 1.
(egvi <- EGVI(crops, 1, 2,3))

```

Visualization time:

```{r}
cortes <- seq(-0.35, 1, by=0.1)
cols <- colores(length(cortes)-1)
##plot(ndvitrend, 2, col=cols, breaks=classbreaks)
plot(egvi, 1, col = cols, breaks=cortes, main = "ExG Vegetation Index")

```

Let’s calculate the NGRDI index:

```{r}
# For the crops image red = 1, green=2, blue = 1.
(ngvi <- NGRDI(crops, 1, 2,3))

```

Visualization time:

```{r}
cortes <- seq(-0.35, 1.0, by=0.1)
cols <- colores(length(cortes)-1)
##plot(ndvitrend, 2, col=cols, breaks=classbreaks)
plot(ngvi, 1, col = cols, breaks=cortes, main = "NGRDI Vegetation Index")

```

## 2. Image segmentation

Let’s read the image using the OpenImageR package:

```{r}
RGB.Color <- readImage("~/giserias/conchalito-vuelo2/conchal_10.tif")
#RGB.Color <- readImage("~/giserias/conchalito-vuelo2/RPubs_crops.jpg")
#RGB.Color <- RGB.Color[, , 1:3] # lee cuatro capas en lugar de tres
```

Let’s use now SLIC for image segmentation. For detailed explanation of the code see the package’s vignette.

```{r}
Region.slic = superpixels(input_image = RGB.Color, method = "slic", superpixel = 80,
   compactness = 30, return_slic_data = TRUE,
   return_labels = TRUE, write_slic = "",
   verbose = FALSE)

```

```{r}
imageShow(Region.slic$slic_data)
```

## 3. Data analysis

```{r}
str(RGB.Color)
```

Let’s get a matrix with NGRDI values:

```{r}
ngvi
egvi
egvi@data@values
ngvi@data@values
ngvi.mat <- matrix(ngvi@data@values,
            nrow = ngvi@nrows,
            ncol = ngvi@ncols, byrow = TRUE)
min(ngvi.mat)
max(ngvi.mat)
```
